Manuscript for MADA Project

### 2024-02-20 products/manuscript/Manuscript.qmd
Emma-Part 2 for Project

Project Part 1: This dataset was obtained from Kaggle.com and was created by Mark Otto and Andrew Fong at MIT. The set has 373 observations for 13 variables covering a broad spectrum associated with sleep and daily routine.

>>>>

Project Part 1: This dataset was obtained from Kaggle.com at this [link](https://www.kaggle.com/datasets/henryshan/sleep-health-and-lifestyle/data) and was created by Mark Otto and Andrew Fong at MIT. The set has 373 observations for 13 variables covering a broad spectrum associated with sleep and daily routine.
